Incentivizing Exploration with Unbiased History

### 2018-10-21 2level.tex
stoc

%!TEX root = main.tex
\section{Warm-up: 2-level Recommendation Policy}
In this section, we are going to show a 2-level recommendation policy that gets sublinear regret.

The 2-level recommendation policy is constructed as following.
In the first level, we run $T_1$ \ALGG of $\GdT$ rounds ``in parallel''. More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups of equal size and agents only observe the history of all previous agents in the same group.
In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
See also Figure \ref{fig:2level} for a graphical view of the information flow.

The idea of this 2-level recommendation policy is simple. We first try to explore all arms enough amount of times in the first level using multiple runs of \ALGG under the guarantee of Lemma \ref{lem:greedy}. After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean.

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};
\end{tikzpicture}
\caption{2-level Recommendation Policy.}
\label{fig:2level}
\end{figure}

\begin{theorem}
\label{thm:2level}
With proper setting of $T_1$, the 2-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret $O(\log(T) \cdot \Delta^{-2})$. 
\end{theorem}

>>>>

%!TEX root = main.tex
\section{Warm-up:  Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a sublinear regret
  rate. The policy essentially follows the ``explore-then-exploit''
  paradigm and consists two phases, which can be described as a
  two-level information graph (as shown in Figure~\ref{fig:2level}).
  In the first level, we perform exploration by simulating $T_1$
  independent runs \ALGG of $\GdT$ rounds. This is done by randomly
  dividing the first $T_1 \cdot \GdT$ agents into $T_1$ groups of
  equal size and each agent only observe the history of all previous
  agents in the same group.  In the second level, we ``exploit'' by
  showing all the remaining agents the entire history of first phase.

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of \ALGG. Since each run of \ALGG
  explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
  ensure that with high probability, every arm is pulled with a
  sufficient number of times. As a result, every agent in the second
  level will pull an arm with mean rewards close to optimal.

}

\iffalse
The 2-level recommendation policy is constructed as following.
In the first level, we run $T_1$ \ALGG of $\GdT$ rounds ``in parallel''. More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups of equal size and agents only observe the history of all previous agents in the same group.
In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
See also Figure \ref{fig:2level} for a graphical view of the information flow.

The idea of this 2-level recommendation policy is simple. We first try to explore all arms enough amount of times in the first level using multiple runs of \ALGG under the guarantee of Lemma \ref{lem:greedy}. After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean. 
\fi

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};
\end{tikzpicture}

\caption{Structure of information graph for the 2-level policy. Each
  red ``box'' is level 1 corresponds to a path connecting a set of
  $T_G$ agents. The entire history in level 1 is then aggregated and
  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}

\begin{theorem}
\label{thm:2level}
With proper setting of $T_1$, the 2-level policy gets expected regret
$O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of
the best arm and second best arm is larger than $\Delta$, we can make
the expected regret $O(\log(T) \cdot \Delta^{-2})$.
\end{theorem}

### 2018-10-21 model.tex
oh yea
stoc

\xhdr{Information flow graph.} We will describe our transitive
policies using a \emph{information flow graph} (and henceforth
\emph{info graph})---a directed graph over the $T$ agents such that if
there is an edge from $u$ to $v$, it means $u\in S_v$. By the property
of transitivity, $S_t$ is the set of nodes that can reach node $t$ in
the info graph.

@@

\xhdr{Agents' behavior.} We model agents with heterogeneity in their
arm selections. In particular, each agent $t$ has a private estimator
that maps the revealed sub-history $H_t$ to a mean reward estimate
$\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$
with the highest estimate. The agents' private estimators are drawn
i.i.d.~from some distribution. For any $t\in[T]$ and $a\in \A$, we
write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of
$a$ and the empirical mean reward of arm $a$ in $H_t$ respectively. If
an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

>>>>

\xhdr{Information flow graph.} We will describe our transitive
policies using a \emph{information flow graph} (and henceforth
\emph{information graph})---a directed graph over the $T$ agents such that if
there is an edge from $u$ to $v$, it means $u\in S_v$. By the property
of transitivity, $S_t$ is the set of nodes that can reach node $t$ in
the info graph.

@@

\xhdr{Agents' behavior.} We model agents with heterogeneity in their
arm selections. In particular, each agent $t$ has a private estimator
that maps the revealed sub-history $H_t$ to a mean reward estimate
$\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$
with the highest estimate. The agents' private estimators are drawn
i.i.d.~from an unknown distribution. For any $t\in[T]$ and $a\in \A$,
we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls
of $a$ and the empirical mean reward of arm $a$ in $H_t$
respectively. If an arm is not pulled in $H_t$, we will let
$\bar{\mu}_a^t = 0$.
